---
title: "group 11 eda"
output:
  html_document:
    df_print: paged
date: '2022-11-08'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(magrittr)
library(readxl)
library(ggplot2)
library(dplyr)
library(hrbrthemes)
library(gapminder)
library(usmap)
library(plotly)
library(tidyr)
```

## Data Cleaning

```{r cars}
strawb <- read_xlsx("strawberries-2022oct30-a.xlsx")
cnames <- colnames(strawb)
x <- 1:dim(strawb)[2]
T <- NULL
for(i in x){T <- c(T, dim(unique(strawb[i]))[1])}
drop_cols <- cnames[which(T == 1)]
strawb %<>% dplyr::select(!all_of(drop_cols))
strawb %<>% arrange(Year, State)
colnames(strawb)
temp1 <- strawb %>% dplyr::select(`Data Item`) %>% distinct()
strawb %<>% separate(col=`Data Item`, into = c("Strawberries", "type", "items", "units"), sep = ",", fill = "right")
temp1 <- strawb %>% dplyr::select(`Strawberries`) %>% 
  distinct()
pr_rec <- grep("STRAWBERRIES - PRICE RECEIVED", 
                  strawb$Strawberries, 
                  ignore.case = T)
type_organic <- grep("organic", strawb$type, ignore.case = T)
items_organic <- grep("organic", strawb$items, ignore.case = T)
Domain_organic <- grep("organic", strawb$Domain, ignore.case = T)
Domain_Category_organic <- grep("organic", strawb$`Domain Category`, ignore.case = T)
same <- (intersect(type_organic, Domain_organic)==
           intersect(type_organic, Domain_organic))
length(same)==length(type_organic)
org_rows <- intersect(type_organic, Domain_organic)
strawb_organic <- strawb %>% slice(org_rows, preserve = FALSE)
strawb_non_organic <- strawb %>% filter(!row_number() %in% org_rows)
temp1 <- strawb_non_organic %>% dplyr::select(type) %>% distinct()
chem_rows <- grep("BEARING - APPLICATIONS", strawb_non_organic$type, ignore.case = T)
chem_rows_1 <- grep("chemical", strawb_non_organic$Domain, ignore.case = T)
ins <- intersect(chem_rows, chem_rows_1)
chem_rows_2 <- grep("chemical", strawb_non_organic$`Domain Category`, ignore.case = T)
ins_2 <- intersect(chem_rows, chem_rows_2)
strawb_chem <- strawb_non_organic %>% slice(chem_rows, preserve = FALSE)
rm(x, T, drop_cols, temp1, r_thiram, r_thiram_1,
   df_carbendazim, df_Bifenthrin, df_methyl_bromide, 
   df_1_3_dichloropropene, df_chloropicrin, df_Telone,
   pr_rec, type_organic, items_organic, Domain_organic,
   Domain_Category_organic, same, org_rows, chem_rows,
   chem_rows_1, chem_rows_2, ins, ins_2, cnames, i)
before_cols = colnames(strawb_chem)
T = NULL
x = length(before_cols)
for(i in 1:x){
  b <- length(unlist(strawb_chem[,i] %>% unique()) )
  T <- c(T,b)
}
drop_cols <- before_cols[which(T == 1)]
strawb_chem %<>% dplyr::select(!all_of(drop_cols))
after_cols = colnames(strawb_chem)
temp1 <- strawb_chem %>% dplyr::select(units) %>% distinct()
strawb_chem %<>% separate(col=`Domain Category`, 
                          into = c("dc1", "chem_name"),
                          sep = ":", 
                          fill = "right")
temp1 <- strawb_chem %>% dplyr::select(chem_name) %>% unique()
length(unlist(temp1))
aa  <- grep("measured in", strawb_chem$items, ignore.case = T)
length(aa)
sum(strawb_chem$Domain == strawb_chem$dc1) == dim(strawb_chem)[1]
strawb_chem %<>% dplyr::select(Year, State, items, units, dc1, chem_name, Value)
strawb_chem %<>% rename(category = units)
strawb_chem$items <- str_remove_all(strawb_chem$items, "MEASURED IN ")
strawb_chem %<>% rename(units = items)
bb  <- grep("CHEMICAL, ", strawb_chem$dc1, ignore.case = T)
length(bb)
chem <- 1:2112
non_chem_rows <- setdiff(chem, bb)
length(non_chem_rows)
temp1 <- strawb_chem %>% slice(non_chem_rows)
rm(temp1, temps, temp3, aa, bb)
strawb_chem$dc1 <- str_remove_all(strawb_chem$dc1, "CHEMICAL, ")
strawb_chem$dc1 %>% unique()
strawb_chem %<>% rename(chem_types = dc1)
strawb_chem$chem_name <- str_remove_all(strawb_chem$chem_name, "\\(")
strawb_chem$chem_name <- str_remove_all(strawb_chem$chem_name, "\\)")
strawb_chem %<>% separate(col = chem_name,
                          into = c("chem_name","chem_code"),
                          sep = "=",
                          fill = "right")
```

## Plots

#1. Focus on Strawb_chem to see the amount change of hazardous chemicals(like Bifenthrin) on strawberries over years.

```{r pressure, echo=FALSE}
Bife <- filter(strawb_chem, chem_code == " 128825" & units == " LB")
ggplot(Bife,mapping = aes(x = Year, y = as.numeric(Value)))+geom_point(alpha = 1, aes(color = State))+labs(title = "Amount of bifenthrin used over time", x = "Year", y ="Amount used in LB per year")

methy <- filter(strawb_chem, chem_code == " 53201" & units == " LB")
ggplot(methy,mapping = aes(x = Year, y = as.numeric(Value)))+geom_point(alpha = 1, aes(color = State))+labs(title = "Amount of methyl bromide used over time", x = "Year", y ="Amount used in LB per year")

Chlo <- filter(strawb_chem, chem_code == " 81501" & units == " LB")
ggplot(Chlo,mapping = aes(x = Year, y = as.numeric(Value)))+geom_point(alpha = 1, aes(color = State))+labs(title = "Amount of chloropicrin used over time", x = "Year", y ="Amount used in LB per year")
```

-   For Bifenthrin, ther amount reaches it's peak at 2019 and then decrease for California. Oregon withheld to avoid disclosing data for individual operations.

-   From the data and plot we could find out only california applied methyl bromide, however, the amount is withheld to avoid disclosing data for individual operations.

-   Floria withheld to avoid disclosing data for individual operations. California utilized this fumigant in large amount except for 2018.

#2. CV that correlated with organic strawberry form 2016 to 2019

```{r}
#cv that correlated with organic strawberry form 2016 to 2019
organic<- filter(strawb,Domain=="ORGANIC STATUS")
str(organic)

ggplot(organic, aes(x = Year, y = as.numeric(organic$`CV (%)`), fill = State)) + 
    geom_point( aes(xend = Year, yend = 0)) +
    geom_point( size=1, color="blue") +
    theme_bw() +
    xlab("")
```

#3. A pie chart of the amount of usage of chemicals for different states, a point chart for changes in years, and the amount of using different chemicals.

```{r}
strawb_new <- filter(strawb, Value != "(NA)", Value != "(D)")
nonorganic <- filter(strawb_new, Domain != "ORGANIC STATUS", Domain != "TOTAL")
ca <- nonorganic %>% 
  filter(Domain %in% c("CHEMICAL, FUNGICIDE", "CHEMICAL, HERBICIDE", 
                       "CHEMICAL, INSECTICIDE", "CHEMICAL, OTHER", "FERTILIZER")) %>%
  filter(State == "CALIFORNIA")

# Non-Organic Strawb Value by State
new_ca <- ca %>% separate(col=`Domain Category`, into = c("Domain1", "chemical_name"),
                          sep = ":",
                          fill = "right")
ggplot(data = strawb_new, aes(x = "", y = as.integer(Value), fill = State)) + 
  geom_bar(stat = "identity") +
  labs(title = "Non-Organic Strawb Value by State")+
  coord_polar("y")
```

```{r}
# the change of chemicals by year
p <- new_ca %>%
  ggplot(aes(Year, Domain, size = as.integer(Value), color = Domain)) +
  geom_point() +
  theme_bw()
ggplotly(p)
```

-   The chemicals did not decrease, it still contains a lot

```{r}
ggplot(new_ca, aes(x = Domain, y = as.integer(Value), fill = Domain)) + 
    geom_segment( aes(xend = Domain, yend = 0)) +
    geom_point( size=4, color="orange") +
    theme_bw() +
    xlab("")

```

-   Fertilizer used the most, other_chemicals follows

-   Herbicide used the least

#4. The subset of 'sales of organic strawberries'. Is there a change in sales as the year pass?

```{r}
#units column = NA -> total sales(CWT,$) of FRESH MARKET AND PROCESSING
#Since we don't have to see the sales of FRESH MARKET AND PROCESSING, let's only remain the total sales.
total <- which(is.na(strawb_organic$units))
sales_organic <- strawb_organic %>% slice(total)

cnames <- colnames(sales_organic) 
x <- 1:dim(sales_organic)[2]
T <- NULL

## Collect number of unique rows in each column
for(i in x){T <- c(T, dim(unique(sales_organic[i]))[1])}
## Use T to select columns to drop -- 
drop_cols <- cnames[which(T == 1)]
## Now, drop the columns with only one unique value.
sales_organic %<>% select(!all_of(drop_cols))
##Let's remove the column State ANSI
sales_organic <- sales_organic %>% select(-'State ANSI')

## remove "MEASURED IN " 
sales_organic$items <- str_remove_all(sales_organic$items, "MEASURED IN ")

##rename
sales_organic <- sales_organic %>% rename(units=items)

## Let's arrange the data frame by units
sales_organic %<>% arrange(units)

#remove (D)
sales_organic <- sales_organic[-which(sales_organic$Value == "(D)"),]

#ready for making graph
sales_organic$Year <- as.character(sales_organic$Year)
sales_organic$Value <- as.numeric(sales_organic$Value)

sales_organic$State <- str_replace(sales_organic$State , "CALIFORNIA", "CA")
sales_organic$State <- str_replace(sales_organic$State , "NEW JERSEY", "NJ")
sales_organic$State <- str_replace(sales_organic$State , "PENNSYLVANIA", "PA")
sales_organic$State <- str_replace(sales_organic$State , "FLORIDA", "FL")
sales_organic$State <- str_replace(sales_organic$State , "OREGON", "OR")
sales_organic$State <- str_replace(sales_organic$State , "NEW YORK", "NY")


#graph : sales for organic strawberries in 2016 and 2019 with $ unit
sales_organic %>% 
  filter(units==" $") %>%
  group_by(Year) %>%
  ggplot(aes(x=State,y=Value,fill=Year))+
  scale_y_log10()+
  geom_col(position = "dodge")+
  labs(y="$")

#graph : sales for organic strawberries in 2016 and 2019 with CWT unit
sales_organic %>% 
  filter(units==" CWT") %>%
  group_by(Year) %>%
  ggplot(aes(x=State,y=Value,fill=Year))+
  scale_y_log10()+
  geom_col(position = "dodge")+
  labs(y="CWT")
rm(cnames,drop_cols,i,T,total,x)

```

```{r}
library(usmap)
library(ggplot2)
sales_organic_2016 <- filter(sales_organic, Year == 2016)
State <- c(06, 12, 34, 36, 41, 42)
cwt_2016 <- c(1446458, 14532, 111, 1012, 5832, 285)
organic_2016 <- data.frame(fips = State, CWT = cwt_2016)
plot_usmap(data = organic_2016, values = "CWT", color = "red") + 
  scale_fill_continuous(name = "CWT", label = scales::comma) + 
  theme(legend.position = "right")

sales_organic_2019 <- filter(sales_organic, Year == 2019)
State <- c(06, 12, 34, 36, 41, 42)
cwt_2019 <- c(1384016, 59905, 208, 2260, 5081, 341)
organic_2019 <- data.frame(fips = State, CWT = cwt_2019)
plot_usmap(data = organic_2019, values = "CWT", color = "red") + 
  scale_fill_continuous(name = "CWT", label = scales::comma) + 
  theme(legend.position = "right")
```

-   From the dataset 'sales_organic', we can verify the increase in sales of organic strawberries from 2016 to 2019 in most states.

-   This means, the popularity of organic sales is getting higher, and it's promising for improving public health in the US.

-   From this result, there should be an effort to implement the policy for boosting the supply of organic strawberries at reasonable prices.
