---
title: "Tnum Assignment 2"
author: "Group 11"
date: "2022-11-10"
output: html_document
---

```{r}
library(devtools)
library(tnum)
library(tidyverse)
#devtools::install_github("arazdow/tnum/tnum", force = TRUE)
tnum.loadLibs()
tnum.authorize(ip="mssp.truenum.com:8080",creds = "yxu662@bu.edu:cougar")
```

## Assignment 2
```{r}
library(tibble)
d1 <- tnum.getAllProperties()
d2 <- tnum.getAllSubjects()
d3 <- tnum.getAllTags()
```


# Massachusetts population with no health insurance
```{r}
x_nhi_mas <- tnum.query("subj:Massachusetts* and prop:population:no_health_insurance and numval:>20000")
xmas <-  mapply(FUN = tnum.addTag,
       guid = x_nhi_mas$id,
       tag = "pop no_health_insurance: large",
       text = "the population of no helath insurance in Massachusetts")
tnum.getTagsOfTn(x_nhi_mas[1,]$id)
kable(x_nhi_mas)
```

```{r}
tn1 <- tnum.postStatement(
  stmt = "The largest number of Massachusetts at Middlesex that not having health insurance is 39401 ",
  notes = "Our first truenumber"
)
```

# Maine population with no health insurance
```{r}
x_nhi_mai <- tnum.query("subj:Maine* and prop:population:no_health_insurance and numval:>10000")
xmai <-  mapply(FUN = tnum.addTag,
       guid = x_nhi_mai$id,
       tag = "pop no_health_insurance: large",
       text = "the population of no helath insurance in Maine")
tnum.getTagsOfTn(x_nhi_mai[1,]$id)
kable(x_nhi_mai)
```
```{r}
tn2 <- tnum.postStatement(
  stmt = "The largest number of Maine at Cumberland that not having health insurance is 16666",
  notes = "Our second true number"
  )
```

# Connecticut population with no health insurance
```{r}
x_nhi_con <- tnum.query("subj:Connecticut* and prop:population:no_health_insurance and numval:>10000")
xcon <-  mapply(FUN = tnum.addTag,
       guid = x_nhi_mai$id,
       tag = "pop no_health_insurance: large",
       text = "the population of no helath insurance in Connecticut")
tnum.getTagsOfTn(x_nhi_con[1,]$id)
kable(x_nhi_con)
```
```{r}
tn3 <- tnum.postStatement(
  stmt = "The largest number of Connecticut at Fairfield that not having health insurance is 78804",
  notes = "Our third true number"
  )
```

# New hampshire population with no health insurance
```{r}
x_nhi_new <- tnum.query("subj:New_Hampshire* and prop:population:no_health_insurance and numval:>5000")
xnew <-  mapply(FUN = tnum.addTag,
       guid = x_nhi_mai$id,
       tag = "pop no_health_insurance: large",
       text = "the population of no helath insurance in New_Hampshire")
tnum.getTagsOfTn(x_nhi_new[1,]$id)
kable(x_nhi_new)
```

```{r}
tn4 <- tnum.postStatement(
  stmt = "The largest number of New hampshire at Hillsborough that not having health insurance is 25235",
  notes = "Our fourth true number"
  )
```

# Rhode Island population with no health insurance
```{r}
x_nhi_rho <- tnum.query("subj:Rhode_Island* and prop:population:no_health_insurance and numval:>1000")
xrho <-  mapply(FUN = tnum.addTag,
       guid = x_nhi_mai$id,
       tag = "pop no_health_insurance: large",
       text = "the population of no helath insurance in NRhode_Island")
tnum.getTagsOfTn(x_nhi_rho[1,]$id)
kable(x_nhi_rho)
```
```{r}
tn5 <- tnum.postStatement(
  stmt = "The largest number of Rhode Island at Washington that not having health insurance is 33911",
  notes = "Our fifth truenumber"
  )
```

# New_Hampshire Population
```{r}
nh_pop <- tnum.query("subj:New_Hampshire* and prop:population and numval:> 100000")
nh1 <- mapply(FUN = tnum.addTag,
       guid = nh_pop$id,
       tag = "county:large",
       text = "the large counties in New Hampshire")
tnum.getTagsOfTn(nh_pop[1,]$id)
kable(nh_pop)

#Hillsborough 
```

```{r}
tn6 <- tnum.postStatement(
  stmt = "the largest number of New_Hampshire Population at Hillsborough is 413035",
  notes = "Our sixth truenumber"
)
```

# Massachusettes Population
```{r}
ma_pop <- tnum.query("subj:Massachusetts* and prop:population and numval:> 700000")
ma1 <- mapply(FUN = tnum.addTag,
       guid = ma_pop$id,
       tag = "county:large",
       text = "the large counties in Massachusetts")
tnum.getTagsOfTn(ma_pop[1,]$id)
kable(ma_pop)

#Middlesex
```

```{r}
tn7 <- tnum.postStatement(
  stmt = "the largest number of Massachusetts Population at Middlesex is 1600842",
  notes = "Our seventh truenumber"
)
```

# Connecticut Population

```{r}
ct_pop <- tnum.query("subj:Connecticut* and prop:population and numval:> 700000")
ct_pop1 <- mapply(FUN = tnum.addTag,
       guid = ct_pop$id,
       tag = "county:large",
       text = "the large counties in Connecticut")
tnum.getTagsOfTn(ct_pop[1,]$id)
kable(ct_pop)

#Fairfield
```

```{r}
tn8 <- tnum.postStatement(
  stmt = "the largest number of Connecticut Population at Fairfield is 943926",
  notes = "Our eighth truenumber"
)
```

# New_Hampshire masters

```{r}
nh_master <- tnum.query("subj:New_Hampshire* and prop:population:masters and numval:> 20000")
nh_master1 <- mapply(FUN = tnum.addTag,
       guid = nh_master$id,
       tag = "master:large",
       text = "the large population of masters in New Hampshire")
tnum.getTagsOfTn(nh_master[1,]$id)
kable(nh_master)

#Hillsborough 
```

```{r}
tn9 <- tnum.postStatement(
  stmt = "the largest number of master in New_Hampshire at Hillsborough is 31606",
  notes = "Our ninth truenumber"
)
```

# Massachusetts masters

```{r}
ma_master <- tnum.query("subj:Massachusetts* and prop:population:masters and numval:> 50000")
ma_master1 <- mapply(FUN = tnum.addTag,
       guid = ma_master$id,
       tag = "master:large",
       text = "the large population of masters in Massachusetts")
tnum.getTagsOfTn(ma_master[1,]$id)
kable(ma_master)

#Middlesex
```

```{r}
tn10 <- tnum.postStatement(
  stmt = "the largest number of master in Massachusetts at Middlesex is 218821",
  notes = "Our tenth truenumber"
)
```

## 10 True Number in One Table
```{r}
df <- tnum.jsonArray(list(tn1, tn2, tn3, tn4, tn5, tn6, tn7, tn8, tn9, tn10))

kable(df)
```